Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-10 docs/ms.tex
Update ms.tex

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error will
affect the variance and bias of this Hierarchical Bayesian method.
In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
However,due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$.
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
The result of bias test and mean square error test is shown in

@@

Several  model fitting  shape measurent methods have been proposed in recent years.
Unlike the average method which merely request a point estimator of galaxy ellipcity,our 
hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity in a Bayesian probability analysis framework.
\begin{itemize}
\item We ...
\item The ...
\item The ...
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error will
affect the variance and bias of this Hierarchical Bayesian method.
In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
However, due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$.
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
The result of bias test and mean square error test is shown in

@@

Several  model fitting  shape measurent methods have been proposed in recent years.
Unlike the average method which merely request a point estimator of galaxy ellipcity, our 
hierachical bayesian approach utilizes the whole likelihood of the galaxy ellipticity in a Bayesian probability analysis framework.
\begin{itemize}
\item We ...
\item The ...
\item The ...
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
